Developing data load and processing

### 2020-08-27 dev/data_preprocessing.Rmd
Anonymization for analysis

@@

```{r}
complete_data <- join_hospital_data(hospital_data)
# TODO transfers
# TODO check:last day vs. breathing data
# MAx. day vs. read columns
# TODO check units (and convert if necessary)
differing_units <- complete_data$marker_data %>% group_by(marker) %>% filter(length(unique(unit)) > 1) %>% 
  group_by(marker, unit) %>% summarise(count = n(), .groups = "drop")

@@

>>>>

TODO: code adverse events, code discontinued_medication_reason

@@

```{r}
complete_data <- join_hospital_data(hospital_data)
# TODO check:last day vs. breathing data
# MAx. day vs. read columns
differing_units <- complete_data$marker_data %>% group_by(marker) %>% filter(length(unique(unit)) > 1) %>% 
  group_by(marker, unit) %>% summarise(count = n(), .groups = "drop")

@@

## Final processing steps

```{r}
no_data_pts <- 
  complete_data$breathing_data %>% group_by(hospital_id, patient_id) %>%
  summarise(count = n(), .groups = "drop") %>%
  filter(count < 1)

if(nrow(no_data_pts) > 0) {
  print(no_data_pts)
  stop("Some patients have no data")
}
```

```{r}
anonymized_data <- anonymize_for_analysis(complete_data)
```

```{r}
for(n in names(anonymized_data) ) {
  write_csv(anonymized_data[[n]], path = here::here("private_data", paste0(n,".csv")))
}
```
